---
title: "p8105_hw1_xc2784"
output: github_document
---

## Problem 1

```{r setup}
library(moderndive)
library(tidyverse)
data("early_january_weather")
```

### Dataset Description

The `early_january_weather` dataset contains hourly meteorological data for LGA, JFK and EWR for the month of January 2013.
It has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. The mean temperature during this period was `r round(mean(early_january_weather$temp), 1)` F.  

Important variables include `origin` (weather station), `year, month, day, hour` (time of recording), `temp` (temperature in F), `dewp` (dew point in F), `humid` (relative humidity), `wind_dir` (wind direction in degrees), `wind_speed` (wind speed in mph), `wind_gust` (wind gust speed in mph) `precip` (precipitation in inches), `pressure`(sea level pressure in millibars) `visib` (visibility in miles),`time_hour`(Date and hour of the recording as a POSIXct date).

```{r scatter}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(
    title = "Temperature over Time",
    x = "Time",
    y = "Temperature (F)",
    color = "Humidity (%)"
  ) 
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

### Scatterplot description

The scatterplot shows that temperature generally increased over the two weeks, with some fluctuations.Humidity tends to be higher at lower temperatures and lower at higher temperatures.

